Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-03-31 paper/paper.tex
Update paper.tex

\subsection[short]{Apparatus}  % Do we want to change this to Equipment? 
% This may not need to be broken into subsections. Will decide before we resubmit. 
Participants used two different Macbook Pros in this study. One Macbook ran the typing test while the other was used for the QBTest. 
The keyboard on the second Macbook was inaccessible as the eye tracker positioning would block the majority of the keys should they have 
taken the typing test and QBTest on a singular device.

>>>>

\subsection[short]{Apparatus}  % Do we want to change this to Equipment? 
% This may not need to be broken into subsections. Will decide before we resubmit. 
Participants used two different MacBook Pros in this study due to the nature of the eye tracker setup. One MacBook Pro was used to administer the QBTest, and it had the eye tracker mounted on it. The positioning of the eye tracker made it challenging to use this MacBook Pro for the typing test.

QBTest MacBook Pro with Eye Tracker: This MacBook Pro was dedicated to conducting the QBTest. It had the eye tracker mounted on it, which made it difficult to access the keyboard for typing. Participants used this MacBook Pro for the QBTest to ensure that the eye tracker could accurately track their eye movements during the test.

Typing Test MacBook Pro: The second MacBook Pro was used for the typing test. Since it did not have the eye tracker mounted on it, participants could easily access the keyboard and perform the typing test without any interference from the eye tracker.

Using two separate MacBook Pros allowed for the independent administration of the QBTest and typing test, ensuring that participants could perform each task without any physical hindrance from the eye tracker.
